---
title: "Software for data science project 2"
author: "Jeremiah Akintomide"
date: "2023-10-14"
output: html_document
---

# Data Cleaning and Preprocessing 


```{r, echo=FALSE}

library(tidyverse)
library(lubridate)
library(forcats)


# Load the BikeSeoul data
bikeseoul <- read.csv("BikeSeoul.csv")

# 1. Remove Unnecessary Columns
bikeseoul <- bikeseoul %>%
  select(-`Visibility..10m.`, -`Dew.point.temperature.C.`, -`Solar.Radiation..MJ.m2.`, -`Rainfall.mm.`, -`Snowfall..cm.`)

# 2. Filter Out Missing Bike Count Data
bikeseoul <- bikeseoul %>%
  filter(!is.na(`Rented.Bike.Count`) & `Rented.Bike.Count` != 0)

# 3. Remove Functioning Day Column
bikeseoul <- bikeseoul %>%
  select(-`Functioning.Day`)

# Rename the columns in BikeSeoul
bikeseoul <- bikeseoul %>%
  rename(
    "Date" = "Date",
    "Count" = "Rented.Bike.Count",
    "Hour" = "Hour",
    "Temperature" = "Temperature.C.",
    "Humidity" = "Humidity...",
    "WindSpeed" = "Wind.speed..m.s.",
    "Season" = "Seasons",
    "Holiday" = "Holiday"
  )

# Convert the "Date" column to a date object
bikeseoul$Date <- as.Date(bikeseoul$Date, format = "%m/%d/%Y")

# Create a new variable FullDate with hour, minute, and second set to zero
bikeseoul$FullDate <- make_datetime(
  year(bikeseoul$Date),
  month(bikeseoul$Date),
  day(bikeseoul$Date),
  hour = bikeseoul$Hour
)

# Set the minute and second to zero
bikeseoul$FullDate <- bikeseoul$FullDate + minutes(0) + seconds(0)

# Change the factor levels of the "Holiday" column
bikeseoul$Holiday <- fct_recode(bikeseoul$Holiday, "Yes" = "Holiday", "No" = "No Holiday")

# Change the order of the factor levels in the "Season" column
bikeseoul$Season <- fct_relevel(bikeseoul$Season, "Spring", "Summer", "Autumn", "Winter")

# View the updated structure of the dataset
str(bikeseoul)


```

## Data Cleaning and Preprocessing for BikeSeoul Dataset

In this section, we describe the steps taken to prepare the BikeSeoul dataset for analysis. The dataset contains information on bike rentals in Seoul, including features like date, hour, temperature, humidity, wind speed, season, and holiday status.

### Step 1: Removing Unnecessary Columns

The initial step involved the removal of irrelevant or redundant columns from the dataset. These columns were omitted:

- `Visibility (10m)`: This column represented visibility in meters, which was not directly relevant to bike rental analysis.
- `Dew Point Temperature (°C)`: Dew point temperature data was excluded as it did not play a central role in the analysis.
- `Solar Radiation (MJ/m2)`: Solar radiation data was eliminated due to limited relevance to bike rental counts.
- `Rainfall (mm)` and `Snowfall (cm)`: Both columns, describing rainfall and snowfall, were excluded from the dataset.

### Step 2: Filtering Missing Bike Count Data

In order to maintain data quality, we filtered out rows with missing or zero bike count data. This step ensured that only records with reliable bike rental information were retained.

### Step 3: Removing "Functioning Day" Column

The "Functioning Day" column was removed since it was not utilized in the analysis. The focus of our analysis primarily revolved around factors related to bike rentals.

### Column Renaming and Date Conversion

For the sake of clarity and consistency, we renamed columns and converted the "Date" column to a date object.

This data cleaning and preprocessing process ensured that the BikeSeoul dataset was well-prepared for subsequent analysis. It involved removing unnecessary data, filtering for reliable bike count information, and conducting necessary column renaming and date conversion to facilitate further modeling and insights.


```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(forcats)

# Load the BikeWashingtonDC data
bikewashingtondc <- read.csv("BikeWashingtonDC.csv")

# Remove the specified columns
bikewashingtondc <- bikewashingtondc %>%
  select(-instant, -yr, -mnth, -weekday, -workingday, -weathersit, -atemp, -casual, -registered)

# Rename the columns in BikeWashingtonDC to match those in Seoul
bikewashingtondc <- bikewashingtondc %>%
  rename(
    "Date" = "dteday",
    "Count" = "cnt",
    "Hour" = "hr",
    "Temperature" = "temp",
    "Humidity" = "hum",
    "WindSpeed" = "windspeed",
    "Season" = "season",
    "Holiday" = "holiday"
  )


# Convert "Season" to a factor with custom levels
bikewashingtondc$Season <- factor(bikewashingtondc$Season, levels = c(1, 2, 3, 4), labels = c("Spring", "Summer", "Autumn", "Winter"))


# Convert "Holiday" to a factor with custom levels
bikewashingtondc$Holiday <- factor(bikewashingtondc$Holiday, levels = c(1, 0), labels = c("Yes", "No"))

# Create the FullDate variable

bikewashingtondc$FullDate <- make_datetime(
  year(bikewashingtondc$Date),
  month(bikewashingtondc$Date),
  day(bikewashingtondc$Date),
  hour = bikewashingtondc$Hour
)

# Set the minute and second to zero
bikewashingtondc$FullDate <- bikewashingtondc$FullDate + minutes(0) + seconds(0)



str(bikewashingtondc)
```

## Data Cleaning and Preprocessing for BikeSeoul Dataset

In this section, we describe the steps taken to prepare the BikeSeoul dataset for analysis. The dataset contains information on bike rentals in Washington, including features like date, hour, temperature, humidity, wind speed, season, and holiday status.

##@ Step 1: Loading the Dataset

We started by loading the BikeWashingtonDC dataset using the `read.csv` function. This dataset contains various attributes related to bike rentals in Washington, D.C.

### Step 2: Removing Unnecessary Columns

To streamline the dataset, we removed several columns that were deemed unnecessary for our analysis. The columns removed included "instant," "yr," "mnth," "weekday," "workingday," "weathersit," "atemp," "casual," and "registered."

### Step 3: Renaming Columns

To ensure consistency and alignment with the Seoul dataset, we renamed the columns using the `rename` function. The column names were changed to match the corresponding attributes in the Seoul dataset.

### Step 4: Converting Categorical Variables

We converted two categorical variables, "Season" and "Holiday," to factors with custom levels. This was done to make the data more interpretable and coherent.

- "Season" was converted into a factor with custom levels "Spring," "Summer," "Autumn," and "Winter."
- "Holiday" was converted into a factor with custom levels "Yes" and "No."

### Step 5: Creating a DateTime Variable

A new variable named "FullDate" was created by combining date and hour information, setting the minutes and seconds to zero. This provides a precise timestamp for the bike rental data.

## Step 6: Summary of the Processed Dataset

We concluded this data preprocessing by examining the updated structure of the BikeWashingtonDC dataset using the `str` function.

---

This data preprocessing aims to harmonize the structure of the BikeWashingtonDC dataset with that of the Seoul dataset, making them compatible for future analyses and comparisons.




# Data visualisation


```{r, echo=FALSE, fig.width=12}

library(ggplot2)
library(gridExtra)
library(scales)

# Create a color-blind friendly palette
color_palette <- c("#1F77B4", "#FF7F0E", "#2CA02C", "#D62728")

# Extract the relevant data for Seoul and Washington
seoul_temp_data <- subset(bikeseoul, select = c(Date, Temperature, Season))
washington_temp_data <- subset(bikewashingtondc, select = c(Date, Temperature, Season))
washington_temp_data$Date <- as.Date(washington_temp_data$Date, format = "%Y-%m-%d")

# Create a line plot for Seoul
seoul_plot <- ggplot(data = seoul_temp_data, aes(x = Date, y = Temperature, linetype = Season, color = Season)) +
  geom_line(size = 1.2) +
  labs(title = "Variation in Air Temperature in Seoul Over a Year",
       x = "Date",
       y = "Temperature (C)") +
  scale_linetype_manual(values = c("Spring" = "solid", "Summer" = "dashed", "Autumn" = "dotdash", "Winter" = "dotted")) +
  scale_color_manual(values = color_palette) +
  theme_minimal() +
  theme(legend.position = "top") +
  guides(linetype = guide_legend(title = "Season")) +
  labs(linetype = "Season")

# Create a line plot for Washington
washington_plot <- ggplot(data = washington_temp_data, aes(x = Date, y = Temperature, linetype = Season, color = Season)) +
  geom_line(size = 1.2) +
  labs(title = "Variation in Air Temperature in Washington Over a Year",
       x = "Date",
       y = "Temperature (C)") +
  scale_linetype_manual(values = c("Spring" = "solid", "Summer" = "dashed", "Autumn" = "dotdash", "Winter" = "dotted")) +
  scale_color_manual(values = color_palette) +
  theme_minimal() +
  theme(legend.position = "top") +
  guides(linetype = guide_legend(title = "Season")) +
  labs(linetype = "Season")

# Display the plots side by side
grid.arrange(seoul_plot, washington_plot,ncol=2 )


```
    
    
**Comment on how air temperature vary over the course of a year?:**

Seasonal Temperature Differences: The graph demonstrates noticeable differences in seasonal temperatures between the two locations. Seoul experiences more extreme temperature variations, with higher temperatures in summer and lower temperatures in winter. In contrast, Washington, D.C., experiences milder temperature variations.

Distinct Seasonal Patterns: For both cities, distinct seasonal patterns are visible. Seoul's summers are warm, followed by spring and autumn, while winter temperatures are considerably lower. Washington, D.C., also exhibits a warmer summer, but the temperature differences between seasons are less pronounced compared to Seoul.

```{r, echo=FALSE, fig.width=10}

# Load required libraries
library(ggplot2)

# Create a color-blind friendly palette
color_palette <- c("#1F77B4", "#FF7F0E", "#2CA02C", "#D62728")

# Create box plots for bike demand by season in Seoul and Washington
seoul_box_plot <- ggplot(data = bikeseoul, aes(x = Season, y = Count, fill = Season)) +
  geom_boxplot() +
  labs(title = "Bike Demand by Season in Seoul",
       x = "Season",
       y = "Count of Rented Bikes") +
  scale_fill_manual(values = color_palette) +  # Use color palette
  theme_minimal()

washington_box_plot <- ggplot(data = bikewashingtondc, aes(x = Season, y = Count, fill = Season)) +
  geom_boxplot() +
  labs(title = "Bike Demand by Season in Washington",
       x = "Season",
       y = "Count of Rented Bikes") +
  scale_fill_manual(values = color_palette) +  # Use color palette
  theme_minimal()

# Display the box plots side by side
grid.arrange(seoul_box_plot, washington_box_plot, ncol = 2)

```

**Bike Demand by Season:**

In Seoul, the median number of rented bikes is highest in Autumn and Summer, indicating that these seasons typically have higher bike rental demand.

In Washington, the median number of rented bikes is highest in Autumn. However, the difference between Summer and Winter is negligible, suggesting that bike rental demand is fairly consistent across these seasons.

In conclusion, Yes, seasons do appear to affect the average number of rented bikes, but the effect varies between cities and seasons.



```{r, echo=FALSE, fig.width=12}

# Load required libraries
library(ggplot2)
library(viridis)

# Create a custom color palette suitable for color blindness
color_palette <- c("#0072B2", "#009E73")

# Create box plots for bike demand on holidays vs. non-holidays in Seoul and Washington
seoul_holiday_box_plot <- ggplot(data = bikeseoul, aes(x = Holiday, y = Count, fill = Holiday)) +
  geom_boxplot() +
  labs(title = "Bike Demand on Holidays vs. Non-Holidays in Seoul",
       x = "Holiday",
       y = "Count of Rented Bikes") +
  scale_x_discrete(labels = c("No" = "Non-Holiday", "Yes" = "Holiday")) +
  scale_fill_manual(values = color_palette) +  # Custom color palette
  theme_minimal()

washington_holiday_box_plot <- ggplot(data = bikewashingtondc, aes(x = Holiday, y = Count, fill = Holiday)) +
  geom_boxplot() +
  labs(title = "Bike Demand on Holidays vs. Non-Holidays in Washington",
       x = "Holiday",
       y = "Count of Rented Bikes") +
  scale_x_discrete(labels = c("No" = "Non-Holiday", "Yes" = "Holiday")) +
  scale_fill_manual(values = color_palette) +  # Custom color palette
  theme_minimal()

# Display the box plots with space between them
grid.arrange(seoul_holiday_box_plot, washington_holiday_box_plot, ncol = 2)

```


### Analysis of Bike Rental Data for Seoul and Washington on do holidays increase or decrease the demand for rented bikes

 To answer the question of whether holidays increase or decrease the demand for rented bikes, I examined box plots for both cities periods.

### Interpretation

From the observed data, it can be concluded that holidays have a notable impact on reducing the demand for rented bikes in both Seoul and Washington. This may be attributed to factors such as reduced commuting needs, different leisure activities, or travel patterns during holidays.

These findings are valuable for bike rental service providers and city planners, as they indicate the need for adjusting bike rental availability and promotion strategies on holidays to account for the lower demand.

In summary, our analysis of the box plots indicates that holidays tend to decrease the demand for rented bikes in both Seoul and Washington, as reflected in the lower medians on holidays compared to non-holidays.


```{r, echo=FALSE}

# Load required libraries
library(ggplot2)

# Create a color-blind friendly palette
color_palette <- c("#1F77B4", "#FF7F0E")

# Create box plots for bike demand by time of day in Seoul and Washington
seoul_box_plot <- ggplot(data = bikeseoul, aes(x = factor(Hour), y = Count, fill = "Seoul")) +
  geom_boxplot(fill = color_palette[1], position = position_dodge(width = 0.8)) +
  labs(title = "Bike Demand by Time of Day for Seoul",
       x = "Hour of the Day",
       y = "Count of Rented Bikes") +
  scale_fill_manual(values = color_palette, name = "City") +
  theme_minimal() +
  guides(fill = guide_legend(title = NULL))

washington_box_plot <- ggplot(data = bikewashingtondc, aes(x = factor(Hour), y = Count, fill = "Washington")) +
  geom_boxplot(fill = color_palette[2], position = position_dodge(width = 0.8)) +
  labs(title = "Bike Demand by Time of Day for Washington",
       x = "Hour of the Day",
       y = "Count of Rented Bikes") +
  scale_fill_manual(values = color_palette, name = "City") +
  theme_minimal() +
  guides(fill = guide_legend(title = NULL))

# Display the box plots side by side
grid.arrange(seoul_box_plot, washington_box_plot, ncol = 1)





```

### Analysis of Bike Rental Data for Seoul and Washington on do holidays increase or decrease the demand for rented bikes

**Seoul**

In Seoul, the graph shows two distinct peaks in bike rental demand: one in the morning (around 8 AM) and another in the evening (around 6 PM). These peaks likely correspond to commuting patterns, as people rent bikes to travel to and from work or school. The demand for rented bikes remains relatively high throughout the day, with a slight dip during midday (around 12 PM to 2 PM).

**Washington**

In Washington, the graph also shows two peaks in bike rental demand, but they are less pronounced than in Seoul. The morning peak occurs around 8 AM, while the evening peak is more spread out between 4 PM and 6 PM. The demand for rented bikes is generally lower in Washington compared to Seoul, particularly during midday and late-night hours.

**Comparing the Two Cities**

The overall pattern of increased demand during commuting hours and decreased demand during off-peak hours is consistent in both cities. However, the magnitude of the peaks and the overall demand levels differ between Seoul and Washington. This could be attributed to various factors, such as differences in commuting patterns, urban infrastructure, or cultural preferences for cycling.

**Conclusion**

The time of day has a substantial impact on the demand for rented bikes in both Seoul and Washington. Peak rental periods occur during morning and evening commuting hours, while off-peak hours are observed during midday and late-night periods. This pattern reflects the influence of commuting patterns and daily activity levels on bike rental demand. The differences in demand levels between the two cities suggest that local factors also play a role in shaping bike rental patterns.


```{r, echo=FALSE, fig.width=12, fig.height=6}


# Load required libraries
library(ggplot2)
library(scales)

# Create a color-blind friendly palette
color_palette <- c("#1F77B4", "#FF7F0E")

# Extract relevant data for Seoul
seoul_weather_data <- subset(bikeseoul, select = c(Count, Temperature, WindSpeed, Humidity))

# Extract relevant data for Washington
washington_weather_data <- subset(bikewashingtondc, select = c(Count, Temperature, WindSpeed, Humidity))

# Create scatterplot for Seoul - Air Temperature
seoul_temp_scatterplot <- ggplot(seoul_weather_data, aes(x = Temperature, y = Count, color = Temperature)) +
  geom_point() +
  labs(title = "Seoul Association Between Bike Demand and Wind Speed, Humidity and Temp",
       x = "Air Temperature (°C)",
       y = "Bike Demand",
       color = "Air Temperature (°C)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Create scatterplot for Seoul - Wind Speed
seoul_wind_scatterplot <- ggplot(seoul_weather_data, aes(x = WindSpeed, y = Count, color = WindSpeed)) +
  geom_point() +
  labs(title = "",
       x = "Wind Speed (km/h)",
       y = "Bike Demand",
       color = "Wind Speed (km/h)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Create scatterplot for Seoul - Humidity
seoul_humidity_scatterplot <- ggplot(seoul_weather_data, aes(x = Humidity, y = Count, color = Humidity)) +
  geom_point() +
  labs(title = "",
       x = "Humidity (%)",
       y = "Bike Demand",
       color = "Humidity (%)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Create scatterplot for Washington - Air Temperature
washington_temp_scatterplot <- ggplot(washington_weather_data, aes(x = Temperature, y = Count, color = Temperature)) +
  geom_point() +
  labs(title = "Washington association Between Bike Demand and Wind, Humidity and Temp ",
       x = "Air Temperature (°C)",
       y = "Bike Demand",
       color = "Air Temperature (°C)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Create scatterplot for Washington - Wind Speed
washington_wind_scatterplot <- ggplot(washington_weather_data, aes(x = WindSpeed, y = Count, color = WindSpeed)) +
  geom_point() +
  labs(title = "",
       x = "Wind Speed (km/h)",
       y = "Bike Demand",
       color = "Wind Speed (km/h)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Create scatterplot for Washington - Humidity
washington_humidity_scatterplot <- ggplot(washington_weather_data, aes(x = Humidity, y = Count, color = Humidity)) +
  geom_point() +
  labs(title = ".",
       x = "Humidity (%)",
       y = "Bike Demand",
       color = "Humidity (%)") +
  scale_color_gradientn(colours = color_palette) +
  theme_minimal()

# Display scatterplots
grid.arrange(seoul_temp_scatterplot, seoul_wind_scatterplot, seoul_humidity_scatterplot, 
             washington_temp_scatterplot, washington_wind_scatterplot, washington_humidity_scatterplot, 
             ncol = 3, padding=15)

```

### Comment on is there an association between bike demand and the three meteorological variables (air temperature, wind speed and humidity)?

## Seoul

The scatter plot for Seoul shows a clear association between bike demand and the three meteorological variables - air temperature, wind speed, and humidity. 

- **Air Temperature**: The data points suggest that as the air temperature increases, the bike demand also increases. This could be due to the fact that warmer temperatures are more conducive for outdoor activities like biking.

- **Wind Speed**: Lower wind speeds seem to be associated with higher bike demand. High wind speeds might make biking more difficult and less enjoyable, hence the lower demand.

- **Humidity**: The scatter plot for humidity shows no clear pattern, indicating that humidity is not a major factor influencing bike demand in Seoul.

## Washington

The scatter plot for Washington shows a similar trend as Seoul with respect to the association between bike demand and the meteorological variables.

- **Air Temperature**: Just like in Seoul, higher air temperatures in Washington are associated with higher bike demand.

- **Wind Speed**: Lower wind speeds are associated with higher bike demand. This is consistent with the observation in Seoul.

- **Humidity**: The scatter plot for humidity in Washington reveals no discernible pattern, suggesting that humidity is not a major factor influencing bike demand.


# Statistical modelling

```{r, echo=FALSE}

# Load the libraries
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)

# Fit linear models for Seoul
seoul_lm <- lm(log(Count) ~ Season + Temperature + Humidity + WindSpeed, data = bikeseoul)
seoul_summary <- glance(seoul_lm)

# Fit linear models for Washington
washington_lm <- lm(log(Count) ~ Season + Temperature + Humidity + WindSpeed, data = bikewashingtondc)
washington_summary <- glance(washington_lm)

# Compare the results
print("Seoul Model Summary:")
print(seoul_summary)

print("Washington Model Summary:")
print(washington_summary)


```
## Model Summary

### Seoul Model

The linear model for Seoul has an R-squared value of 0.494, indicating that approximately 49.4% of the variance in the log count can be explained by the predictors. The adjusted R-squared value, which adjusts for the number of predictors, is consistent at 0.494. The low value of sigma (0.828) suggests that the model fits the data well, and the F-statistic (1377) with a p-value of 0 indicates that the model is statistically significant. The model includes 6 degrees of freedom, and the log-likelihood is -10406. The AIC (Akaike Information Criterion) and BIC (Bayesian Information Criterion) values are 20827 and 20884, respectively.

### Washington Model

In contrast, the linear model for Washington has a lower R-squared value of 0.278, indicating that the predictors explain only 27.8% of the variance in the log count. The adjusted R-squared is also 0.278. The sigma value (1.26) is higher than in the Seoul model, suggesting less precise fits. However, the F-statistic (1115) with a p-value of 0 indicates that the model is statistically significant. Similar to the Seoul model, the Washington model has 6 degrees of freedom. The log-likelihood is -28714, and the AIC and BIC values are 57444 and 57506, respectively.

## Comparison and Discussion

The Seoul model appears to provide a better fit for the data, with a higher R-squared value and a lower sigma value, indicating better model accuracy. Both models are statistically significant, with very low p-values for the F-statistics.

The differences in R-squared values between the two models suggest that the predictors explain a larger portion of the variance in bike counts in Seoul compared to Washington. This may indicate that other unmeasured factors have a stronger influence on bike demand in Washington, making the model less predictive.

## Conclusion

In summary, the linear models for Seoul and Washington datasets provide valuable insights into the relationship between season, air temperature, humidity, wind speed, and bike demand. While the Seoul model demonstrates a stronger predictive power, further investigation may be required to uncover the unique factors influencing bike rentals in Washington.



```{r, echo=FALSE}

# Fit the linear model 
seoul_model <- lm(log(Count) ~ Season + Temperature + Humidity + WindSpeed, data = bikeseoul)
washington_model <- lm(log(Count) ~ Season + Temperature + Humidity + WindSpeed, data = bikewashingtondc)

# Calculate 97% confidence intervals for coefficients
seoul_ci <- confint(seoul_model, level = 0.97)
washington_ci <- confint(washington_model, level = 0.97)

# Display the confidence intervals
cat("Seoul Model 97% Confidence Intervals:\n\n")
print(seoul_ci)

cat("\nWashington Model 97% Confidence Intervals:\n\n")
print(washington_ci)


```

### Comment on Confidence Intervals

The reliability of a confidence interval can be assessed based on its range and whether it crosses zero. 

For the **Seoul model**, all variables except `SeasonSummer` have confidence intervals that do not cross zero, suggesting they are statistically significant at the 97% confidence level. However, the `SeasonSummer` variable has a confidence interval that crosses zero (-0.067553139 to 0.07476072), indicating it is not statistically significant at this level.

For the **Washington model**, all variables have confidence intervals that do not cross zero, suggesting they are statistically significant at the 97% confidence level. However, the intervals for `Temperature` and `Humidity` are quite wide, indicating less precision in these estimates.

In conclusion, while most variables in both models appear to be statistically significant, there may be some concerns about the precision of estimates for `SeasonSummer` in the Seoul model and `Temperature` and `Humidity` in the Washington model.


```{r, echo=FALSE}

# Predicting for Seoul
seoul_values <- data.frame(
  Season = "Winter",
  Temperature = 0,
  Humidity = 0.20,
  WindSpeed = 0.5
)

seoul_prediction <- predict(seoul_model, newdata = seoul_values, interval = "prediction", level = 0.90)

# Predicting for Washington
washington_values <- data.frame(
  Season = "Winter",
  Temperature = 0,
  Humidity = 0.20,
  WindSpeed = 0.5
)

washington_prediction <- predict(washington_model, newdata = washington_values, interval = "prediction", level = 0.90)

cat("Seoul Predictions and Prediction Intervals:\n")
print(seoul_prediction)

cat("\nWashington Predictions and Prediction Intervals:\n")
print(washington_prediction)


```
## Predicted Bike Rentals in Winter

### Seoul
For Seoul, the model predicts that during winter, when the air temperature is freezing at 0°C, with light wind (0.5 m/s) and a humidity of 20%, the expected number of rented bikes is approximately 6.36. The 90% prediction interval for this estimate ranges from 4.99 to 7.72. This means that we can be reasonably confident that the actual number of rented bikes in this scenario falls within this interval.

### Washington
In the case of Washington, the model predicts that during winter, under similar conditions (0°C air temperature, 0.5 m/s wind speed, and 20% humidity), the expected number of rented bikes is around 4.29. The 90% prediction interval for this estimate spans from 2.21 to 6.36. As with Seoul, this prediction interval provides a reasonable level of confidence in the accuracy of the prediction.

It's important to note that these predictions are based on the linear models developed earlier and rely on the assumption that the models are trustworthy. The actual number of rented bikes may vary, but these predictions provide valuable insights into the expected bike rentals in different weather conditions.

